\documentclass[main.tex]{subfiles}
\begin{document}

Imagine the world without car. In fact, no, we can not imagine that. Car is an important transportation medium that use for our daily commuting purpose. It is a convenience. However, it is inevitable that the consequences of using car for commuting also lead to the accidents occurring almost daily basis around in our environment. The car crash statistics \cite{crashstat1, crashstat2, crashstat3} show that it is never going away and the key reason always being a driver behind the steering wheel; and how does this person make every active-decisions do really matter most. In this context, we built a smart elegant device that could actively advice a driver to become a more safer driver.
\\

In this paper, we explored a solution for a person to become a good behaving driver. We introduced an intelligent device called \textbf{SEDA} which easily fitted into a driver eye wear, glasses or head gear. We further presented that the system comprise of distributed computing components such as the SEDA \textbf{Base App} - a mobile app to configure the device and SEDA \textbf{Backend Cloud Service} for intelligence processing. The overall system architecture aimed to harness the power of Machine Learning techniques to classify the data acquired from SEDA and train the model on a driver behaviour to produce a safer driving profile. This profile were then loaded onto the SEDA device and gave advice based on the difference between the loaded profile and the actual active decision making of a driver.
\end{document}